MultiDataImportPico

### 2023-12-06 Code/MultiDataImportPico.Rmd
Added library(photobiologyWavebands) for WL colors

-move filter for negative OD to point of log curve fitting Filtering
negative points needed for current noise filtering, so placed just
before noise filtering; with more sophisticated noise filtering -add
dynamic extraction of StartTime from first row of AbsTime Done

@@

```{r load libraries}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(broom)
library(zoo)
library(data.table)
library(googledrive)
library(googlesheets4)

@@

#set Photobiology colors
```{r set colours}
MyWavelengths = c(405, 450, 475, 530, 615, 660, 730, "WW")
MCMIXColours = c("violet", "darkblue", "dodgerblue", "green","orange","red","purple", "black")

@@

# List MultiCulti files

for Project that are saved in DataIn

@@

#List files in the extracted folder with a ".asc" extension
# MCFiles <- unzip(DataIn, list = TRUE)
# MCFiles <- MCFiles[grepl(".csv$", MCFiles$Name), "Name"]
# print(MCFiles)

@@

# Set Target File

Could implement function to list difference between
unique(GrowthSummaryAppend\$Filename) and MultiFiles if needed later;
scan visually to set TargetFile for now.

```{r set TargetFile}

TargetFile <- "20211223_PICO_MCMIX006_RUN42.csv"

# This opens a compressed file without decompressing.
TargetData <- read_csv(unz(DataIn, TargetFile),  skip = Skip, id = "path", col_names = c("key", "time", "abs-time", "value")) %>% 
  separate(col = path, into = c("path", "Filename"), sep = ":")

# TargetFileName <- str_remove(string = TargetFile, pattern = ".csv")
# 
# TargetFileName

@@

#extract ExpDate for matching with Catalog
TargetData <- TargetData %>% 
    mutate(ExpDate = str_extract(Filename, "/202[:digit:][:digit:][:digit:][:digit:][:digit:]_"),
           ExpDate = ymd(str_extract(ExpDate, "202[:digit:][:digit:][:digit:][:digit:][:digit:]")))

@@

Run this chunk only for tubes with OD680 and/or OD720 < 0
This will keep record of tubes even if they did not grow or had negative growth. These tubes get filtered out later if you do not run this chunk
Remember to comment out after use 
```{r, Add dummy points if a tube has OD values less than zero}

# TargetDataMeta <- TargetDataMeta %>%
# mutate(OD680 = if_else(Tube == 1, 0.005, OD680),
#        OD720 = if_else(Tube == 1, 0.003, OD720))

Run this chunk if some tubes have poor data
This is bad practice;
Only use if light recordings were actually wrong
Consider a rule-based filtering to eliminate points after curve reaches peak
```{r filter aberrant tube(s)}
# TargetDataMeta <- TargetDataMeta %>%
#   filter(Tube != 1) %>%
#   filter(Tube != 8)
# 
# TargetDataMeta5 <- TargetDataMeta %>%
#   filter(Tube == 5,
#          time <= 300)
# 
# TargetDataMeta <- TargetDataMeta %>%
#   filter(Tube != 5) %>%
#   rbind(., TargetDataMeta5)
# 
# TargetDataMeta %>% ggplot() +
#   geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.1) +
#   geom_point(aes(x = time, y = OD720), size = 0.01, alpha = 0.1, colour = "black") +
#   geom_point(aes(x = time, y = Actinic_par/1000),  colour = "orange", size = 0.0001) +
#   geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
#   geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
#   #scale_x_continuous(breaks=seq(0, 800, by = 125)) +
#   #coord_cartesian(xlim = c(-10, 800)) +
#   #scale_colour_manual(values = MCMIXColours) +
#   labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", subtitle = "Growth Light (µE); Strain; ID; Tube") +
#   facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Tube), as.factor(Par_ue),Strain, ID)) +
#   theme_bw() +  
#   labs(colour = "Actinic PAR (nm)")

@@

#moving average screen
MovAvgScreen <- 6
MovAvgWindow <- 20

@@

#labelling dynamically offset from data traces.
#use 'median' for 'x' and OD680 + offset for 'y'
ExpandTube = 1
OD680_x = median(TargetDataMetaFilter$time)
OD720_x = median(TargetDataMetaFilter$time) 
Light_x = max(TargetDataMetaFilter$time) + 100

>>>>

-move filter for negative OD to point of log curve fitting Filtering
negative points needed for current noise filtering, so placed just
before noise filtering; with more sophisticated noise filtering

@@

```{r load libraries}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(broom)
library(zoo)
library(data.table)
library(googledrive)
library(googlesheets4)
library(photobiologyWavebands)

@@

#set Photobiology colors
```{r set colours}
MyWavelengths = c(405, 445, 470, 530, 620, 660, 730, "WW")
MCMIXColours = c(c(w_length2rgb(405), w_length2rgb(445), w_length2rgb(470), w_length2rgb(530),            w_length2rgb(620), w_length2rgb(660), w_length2rgb(730), "black"))

# MyWavelengths = c(450, 530, 660, "WW")
# MCMIXColours = c(w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "black")

@@

# List MultiCulti files for Project that are saved in DataIn

@@

#List files in the extracted folder with a ".asc" extension
MCFiles <- unzip(DataIn, list = TRUE)
MCFiles <- MCFiles[grepl(".csv$", MCFiles$Name), "Name"]
print(MCFiles)

@@

# Set Target File
```{r set TargetFile and read csv}

TargetFile <- "20221021_PICO_MCMIX006_RUN96.csv"

# This opens a compressed file without decompressing.
TargetData <- read_csv(unz(DataIn, TargetFile),  skip = Skip, id = "Path", col_names = c("key", "time", "abs-time", "value")) %>% 
  separate(col =Path, into = c("Path", "Filename"), sep = ":")

TargetFileName <- str_remove(string = TargetFile, pattern = ".csv")

TargetFileName

@@

#extract ExpDate for matching with Catalog
TargetData <- TargetData %>% 
    mutate(ExpDate = str_extract(Filename, "202[:digit:][:digit:][:digit:][:digit:][:digit:]_"),
           ExpDate = ymd(str_extract(ExpDate, "202[:digit:][:digit:][:digit:][:digit:][:digit:]")))

@@

@@

#moving average screen
MovAvgScreen <- 6 # 6
MovAvgWindow <- 20 # 20

@@

#labelling dynamically offset from data traces.
#use 'median' for 'x' and OD680 + offset for 'y'
ExpandTube = 2

OD680_x = median(TargetDataMetaFilter$time)
OD720_x = median(TargetDataMetaFilter$time) 
Light_x = max(TargetDataMetaFilter$time) + 100
